\textsf{Are large language models superhuman chemists?}

### 2024-10-19 src/tex/sections/manually_sources_table.tex
first additions

Solid state chemistry & Based on lectures published on the YouTube channels "Material Universe", "Advanced Cyberinfrastructure Training at RPI", "Phase Diagrams in Materials Science and Engineering" && 9\\

>>>>

Solid state chemistry & Based on lectures published on the YouTube channels Materials Universe, Advanced Cyberinfrastructure Training at RPI, Phase Diagrams in Materials Science and Engineering" && 9\\
